---
title: "IT-Based Management Summary"
author: "Group 06"
date: "11 12 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("xts", repos="http://cloud.r-project.org")


```

## Forecasting and Probalistic Budgeting: Sales Volume Context (Learning with Case Studies)
\section{Use Case}
It is about Candle Manufacturing Inc. company, which produce three different candles like molded candles, solid candles and pulled candles. The company needs to setup the annual sales budget for the next year. To accomplish this, the traditional \textit{time series-based forecasting} methods are applied and two new approaches has been introduced: \newline
\textit{multinominal reggression-based} \newline
\textit{stochastic process-based forecasting of time series}\newline
To answer question about sales volumes that can expected for next year, the R software package are used as we can 
\begin{itemize}
\item perform a traditional time series analysis and use the model for \textbf{time series-based forecasting} for the next year
\item use timely intervals and perform a \textbf{regression-based forecasting}
\item read monthly sales from transactional data
\item perform a \textbf{stochastic process-based forecasting}
\item derive year-end forecast in fixed-event form
\item budget-forecast deviation with p-value to perform adjustments
\end{itemize}

\section {Problem Statement}
As there is uncertainity in business environment, the future predictation of sales volumes is also uncertain and time series-based approch forecast data with the help of historical data. It is not clear which time-based approch should be used in R to produce unbiased data. The two new approaches that are mentioned above allow additional forecast updating which are not possible in time series-based approches. Updating feature is very important in the fixed-event forecasting\footnote{ In the management control the fixed-event forecasts are the year-end forecasts} context as fixed time period is considered over time leading to a successively reducing of the lead time. 
\section {Contribution}
Traditional time series analysis covers the range between decomposition approaches, where non-stationary trends and seasonalities are included, and stationary ARIMA approaches. By introducing new modeling techniques in form of the multinomial regression-based and the stochastic processbased forecasting methods the time series modeling repertoire can be extended in
an effective and easy to grasp way.\newpage
\textbf{Result} 
\newline Multinomial regression-based and stochastic processbased forecasting are mathematically defined and statistically calibrated.
\section{Research Methodology}
The new artifacts are mathematically modeled and their applications are demonstrated in numerical examples.
\section{Research literature}
Hyndman Rob/Athanasopoulos George: Forecasting Principles and
Practice \newline
Lawrence Michael/O'Connor Marcus: Sales forecasting updates:
how good are they in practice?

\newpage
\section{Implementation}
\subsection{Task 1}
Importing and analyzing daily sales data and plotting of xSD01.xts
```{r Plotxts, collapse=TRUE}
library(xts)
xSD01.xts<-readRDS("DataCMI")
str(xSD01.xts)
plot(xSD01.xts, main="Daily sales volumes \n Overall ABC=Blue,  A=Black,  B=red, C=Green")


```

\subsection{Task 2}
 Forecasting daily sales volumes by using automated procedures in forecasting packages
```{r forcast, collapse=TRUE, fig.height = 3, fig.width = 5}
library(forecast)
plot(forecast(as.ts(xSD01.xts)))
plot(forecast(as.ts(xSD01.xts),100))
xSD01.fc<-forecast(as.ts(xSD01.xts),100)
attributes(xSD01.fc)

```



```{r}
xSD01.fc$method
xSD01.fc$method
```
Interpretation: Planning horizon (plan period) of 100 days already shows exploding
uncertainties of ABC, B and C
\subsection{Task 3}
Including additional (predictable) variables into the TS data set

```{r AdditionalVariables}
xSD01Ext.xts<-NULL # Extracting date information from xts-object
xSD01Ext.xts<-xSD01.xts
xSD01Ext.xts$Year<-as.factor(format(index(xSD01.xts),"%Y"))
xSD01Ext.xts$Quarter<-as.factor(quarters(index(xSD01.xts)))
xSD01Ext.xts$Month<-format(index(xSD01.xts),"%m")
xSD01Ext.xts$wDay<-format(index(xSD01.xts),"%u")
```
\subsection{Task 4}
 Performing numeric regressions
Numeric regression: Regressing daily sales volumes against numeric variables

```{r NumericRegression}
xSD01ABC.svlm <- NULL # Single variable linear model (svlm)
xSD01ABC.svlm <- lm(ABC~wDay,xSD01Ext.xts)
summary(xSD01ABC.svlm)
```
\newpage
\subsection{Task 5}
Performing multinomial regressions
Multinomial (factor) regression: Regressing daily sales volumes against categorical
variables

```{r Factor}
xSD01ABC.sflm <- NULL # Single factor linear model (sflm)
xSD01ABC.sflm <- lm(ABC~as.factor(wDay),xSD01Ext.xts)
summary(xSD01ABC.sflm)
```

```{r attributes}
attributes(xSD01ABC.sflm)
```

```{r plot, collapse=TRUE, fig.height = 3, fig.width = 5}
plot(xSD01ABC.svlm$residuals) # Plotting svlm & sflm residuals
plot(xSD01ABC.sflm$residuals)
```

\subsection{Task 6}
 Performing numeric and factor regressions

```{r SingleVariables, collapse=T, fig.height=3, fig.width=5}
 xSD01ABC1.svlm <- NULL # Single linear regression
 xSD01ABC1.svlm <- lm(ABC~Month,xSD01Ext.xts)
 summary(xSD01ABC1.svlm)
 
 xSD01ABC1.sflm <- NULL # Single linear factor regression
 xSD01ABC1.sflm <- lm(ABC~as.factor(Month),xSD01Ext.xts)
 summary(xSD01ABC1.sflm)
 
 plot(xSD01ABC1.svlm$residuals)
 plot(xSD01ABC1.sflm$residuals)

```

\subsection{Task 7}
Performing multi-factor regressions

```{r Multi, collapse=T, fig.height=3, fig.width=5}
xSD01ABC.mflm <- NULL # Multi-factor linear regression
xSD01ABC.mflm <- lm(ABC~as.factor(wDay)+as.factor(Month)+as.factor(Year),xSD01Ext.xts)
summary(xSD01ABC.mflm)

 plot(xSD01ABC.mflm$residuals)
```

\subsection{Task 8}
Performing multi-factor regressions 

```{r multi, collapse=T, fig.height=3, fig.width=5}
xSD01ABC1.mflm <- NULL # Multi-factor multinomial linear regression
xSD01ABC1.mflm <- lm(ABC~as.factor(wDay)+as.factor(Month)*as.factor(Year),xSD01Ext.xts)
summary(xSD01ABC1.mflm)

plot(xSD01ABC1.mflm$residuals)

```

\subsection{Task 9}
Multinomial regression-based forecasting the daily sales volumes for the next year

```{r regressionBasedOnNextYear, collapse=T, fig.height=3, fig.width=5}
 PlanPeriod.xts<-NULL # Generating an indexed xts-object
 PlanPeriod.xts<-as.xts(seq(as.Date("2022-01-01"),
 as.Date("2022-12-31"),by='day'))
 PlanPeriod.xts$Year<-c(2)
 PlanPeriod.xts$Month<-as.factor(format(index(PlanPeriod.xts),"%m"))
 PlanPeriod.xts$wDay<-as.factor(format(index(PlanPeriod.xts),"%u"))
 PP.xts<-NULL
 PP.xts<-subset(PlanPeriod.xts,!(PlanPeriod.xts$wDay %in% c(6,7)))

```

\subsection{Task 10}
Multi-factor regression-based forecasting

```{r perdiction, collapse=T, fig.height=3, fig.width=5}
 xSD01ABC1.mffc<-NULL # Generating predictions
 xSD01ABC1.mffc<-predict(xSD01ABC1.mflm,PP.xts,interval = "confidence")
 head(xSD01ABC1.mffc)
  xSD01ABC1.mffc[1,1]
  xSD01ABC1.mffc[1,2] # lower (lwr) bound
  xSD01ABC1.mffc[1,3] # upper (upr) bound
  sum(xSD01ABC1.mffc[,1]) # Sum of sales forecasts
  apply.quarterly(xSD01ABC1.mffc[,1],FUN = sum)# Quarterly forecasts
  apply.monthly(xSD01ABC1.mffc[,1],FUN = sum) # Monthly forecasts
  
```

Historical calibration problem: 1-year sales forecast of 170750.5 is due to the
historical calibration similar to last years??? sales volumes
```{r , collapse=T, fig.height=3, fig.width=5}
 plot(xSD01ABC1.mffc[,1],type="l") # Plotting predictions
 plot(cumsum(xSD01ABC1.mffc[,1]),type="l")
 lines(cumsum(xSD01ABC1.mffc[,2]))
 lines(cumsum(xSD01ABC1.mffc[,3]))
```

Plotting quaterly and monthly predictions:

```{r,  collapse=T, fig.height=3, fig.width=5}
plot(cumsum(apply.quarterly(xSD01ABC1.mffc[,1],FUN = sum)),type="b")#Q
lines(cumsum(apply.quarterly(xSD01ABC1.mffc[,2],FUN = sum)),type="b")
lines(cumsum(apply.quarterly(xSD01ABC1.mffc[,3],FUN = sum)),type="b")
plot(cumsum(apply.monthly(xSD01ABC1.mffc[,1],FUN = sum)),type="b") #M

```


\subsection{Task 11}
Quarterly xts-time series xSQ01.xts: Generating lower frequency data (e.g.
quarterly sales volumes) via aggregating daily data by using the apply.quarterly() function

```{r, collapse=T, fig.height=3, fig.width=5}

 xSQ01.xts<-apply.quarterly(xSD01.xts$A,sum) # Quarterly sales volumes
 xSQ01.xts<-cbind(xSQ01.xts,apply.quarterly(xSD01.xts$B,sum),
 apply.quarterly(xSD01.xts$C,sum),apply.quarterly(xSD01.xts$ABC,sum))
 xSQ01.xts
 apply.yearly(xSD01.xts$ABC,sum)
 
 plot(xSQ01.xts)
```


\subsection{Task 12}
Regressing the quarterly sales volumes (analogously to the daily sales volumes)
w.r.t. predictable calendar information (e.g. quarters) in form of categorical variables

```{r, collapse=T, fig.height=3, fig.width=5}
 xSQ01Ext.xts<-NULL # Extending the quarterly data base
 xSQ01Ext.xts<-xSQ01.xts
 xSQ01Ext.xts$Quarter<-as.factor(quarters(index(xSQ01.xts)))
 xSQ01Ext.xts
xSQ01ABC.sflm <- NULL # Single-factor linear regression
xSQ01ABC.sflm <- lm(ABC~as.factor(Quarter),xSQ01Ext.xts)
summary(xSQ01ABC.sflm)

```

\subsection{Task 13}
Regressing quarterly sales data without (w/o) intercept term

```{r, collapse=T, fig.height=3, fig.width=5}
xSQ01ABC1.sflm <- NULL # Single factor linear model
xSQ01ABC1.sflm <- lm(ABC~0+as.factor(Quarter),xSQ01Ext.xts)
summary(xSQ01ABC1.sflm)
attributes(xSQ01ABC1.sflm)
sum(xSQ01ABC1.sflm$coefficients)
plot(xSQ01ABC1.sflm)
xSQ01ABC1.sflm$model
model.matrix(xSQ01ABC1.sflm)
```



\subsection{Task 14}
Modeling quarterly sales volumes as Gaussian stochastic processes which are
completely specified by the mean vector and the volatility vector in the case of independently distributed sales volumes in the different quarters

```{r, collapse=T, fig.height=3, fig.width=5}
# Defining and filling of two matrices and an array
 xSQ01ABC_BLY.m<-matrix(coredata(xSQ01.xts[1:4,4]),1,4,byrow=T)
 dimnames(xSQ01ABC_BLY.m)<-list(c("ABC"),c("Q1","Q2","Q3","Q4"))
 xSQ01ABC_LY.m<-matrix(coredata(xSQ01.xts[5:8,4]),1,4,byrow=T)
 dimnames(xSQ01ABC_LY.m)<-list(c("ABC"),c("Q1","Q2","Q3","Q4"))
 xSQ01ABC.a<-array(c(xSQ01ABC_LY.m,xSQ01ABC_BLY.m),dim=c(1,4,2))
 dimnames(xSQ01ABC.a)<-list(c("ABC"),c("Q1","Q2","Q3","Q4"),c("LY","BLY"))
 t(xSQ01ABC.a[1,,])
 
 
# Calibrating the mean vector (location parameters)
 E_xSQ01ABC.m<-matrix(0,1,4)
 for(j in 1:4) E_xSQ01ABC.m[1,j]<-mean(xSQ01ABC.a[1,j,])
 dimnames(E_xSQ01ABC.m)<-list(c("ABC"),c("Q1","Q2","Q3","Q4"))
 E_xSQ01ABC.m
 
# Calibrating the volatility vector (dispersion parameters)
 V_xSQ01ABC.m<-matrix(0,1,4)
 for(j in 1:4) V_xSQ01ABC.m[1,j]<-sd(xSQ01ABC.a[1,j,])
 dimnames(V_xSQ01ABC.m)<-list(c("ABC"),c("Q1","Q2","Q3","Q4"))
 V_xSQ01ABC.m 
 
  CV_xSQ01ABC.m<-V_xSQ01ABC.m/E_xSQ01ABC.m # Coefficient of variation
  CV_xSQ01ABC.m
  
   CV_xSQ01ABC1.m<-CV_xSQ01ABC.m
 CV_xSQ01ABC1.m[CV_xSQ01ABC1.m<0.05]<-0.05 # Setting min. CV to 5 %
 CV_xSQ01ABC1.m
 
  V_xSQ01ABC1.m<-V_xSQ01ABC.m
 V_xSQ01ABC1.m<-CV_xSQ01ABC1.m*E_xSQ01ABC.m
 V_xSQ01ABC1.m
 
 Sales<-seq(20000, 70000, length=100) # Normal density distributions
 plot(Sales,dnorm(Sales,E_xSQ01ABC.m[2],V_xSQ01ABC1.m[2]),col="red")
 lines(Sales,dnorm(Sales,E_xSQ01ABC.m[1], V_xSQ01ABC1.m[1]),col="black")
 lines(Sales,dnorm(Sales,E_xSQ01ABC.m[3],V_xSQ01ABC1.m[3]),col="green")
 lines(Sales,dnorm(Sales,E_xSQ01ABC.m[4],V_xSQ01ABC1.m[4]),col="blue")
 legend("topright", legend=c("Q1","Q2","Q3","Q4"),col=1:4,lty=1)
 
  plot(Sales,dnorm(Sales,E_xSQ01ABC.m[2],V_xSQ01ABC1.m[2]), # Mean/Vola
 col="red",type="l",ylab="Density")
 lines(Sales,dnorm(Sales,E_xSQ01ABC.m[1],V_xSQ01ABC1.m[1]),col="black")
 lines(Sales,dnorm(Sales,E_xSQ01ABC.m[3],V_xSQ01ABC1.m[3]),col="green")
 lines(Sales,dnorm(Sales,E_xSQ01ABC.m[4],V_xSQ01ABC1.m[4]),col="blue")
 legend("topright", legend=c("Q1","Q2","Q3","Q4"),col=1:4,lty=1)
```


\subsection{Task 15}
Probabilistic Budgeting: Stochastic process modeling allows calculating the density function of the annual sales volumes (probabilistic budgeting) analytically by
temporally aggregating the mean vector elements with the linear form and the volatility vector elements with the quadratic form

```{r, collapse=T, fig.height=3, fig.width=5}
 PlanTrajectABC<-cumsum(E_xSQ01ABC.m) # Linear temp. aggregation
 PlanTrajectABC

 plot(PlanTrajectABC)

 BudgetABC<-PlanTrajectABC[4] # Setting the sales budget
 BudgetABC


 PlanVolaABC<-sqrt(cumsum((V_xSQ01ABC.m)^2)) # Quadratic temp. aggreg.
 PlanVolaABC

 lines(PlanTrajectABC+PlanVolaABC)
 lines(PlanTrajectABC-PlanVolaABC)

 PlanVolaABC1<-sqrt(cumsum((V_xSQ01ABC1.m)^2)) # Volatility adjustment
 PlanVolaABC1

 plot(PlanTrajectABC)
 lines(PlanTrajectABC+PlanVolaABC1)
 lines(PlanTrajectABC-PlanVolaABC1)

# Trajectory and corridor plotting
 plot(PlanTrajectABC,col=1:4,xlim=c(1,4),ylim=c(0,200000),xaxt='n',
 xlab = "Future Quarters", ylab = "Cumulated sales")
 axis(1, at = seq(1, 4, by = 1))
 lines(PlanTrajectABC+PlanVolaABC)
 lines(PlanTrajectABC-PlanVolaABC)
# Density function plotting
 plot(seq(160000, 180000, length=100), dnorm(seq(160000, 180000,
length=100),PlanTrajectABC[4],PlanVolaABC[4]), type="l",
 xlab="Sales", ylab="Density", main="plot()") # Density plot ???ABC
 plot(seq(160000, 180000, length=100), pnorm(seq(160000, 180000,
length=100),PlanTrajectABC[4],PlanVolaABC[4])) # Cum.Dens.plot ???ABC
 plot(seq(160000, 180000, length=100), dnorm(seq(160000, 180000,
length=100),PlanTrajectABC[4],PlanVolaABC1[4])) # Density plot ???ABC1
# Mean (location) and volatility (dispersion) parameter plotting
 plot(CV_xSQ01ABC1.m,E_xSQ01ABC.m,col=1:4,ylim=c(0,70000),
 xlim=c(0,5000), xlab = "Sales at risk", ylab = "Expected sales")
 legend("topright", legend=c("Q1","Q2","Q3","Q4"),col=1:4,lty=1)

```


\subsection{Task 16}

 Year-end forecasting and probabilistic control over time
 
```{r, collapse=T, fig.height=3, fig.width=5}
 AA_xSQ01ABC.m<-matrix(0,1,4) # Accumulated Actual
 RE_xSQ01ABC.m<-matrix(0,1,4) # Remaining Expectations
 CF_xSQ01ABC.m<-matrix(0,1,4) # Conditional Forecast
 BFD_xSQ01ABC.m<-matrix(0,1,4) # Budget-Forecast Deviation
 BFDra_xSQ01ABC.m<-matrix(0,1,4) # BFD risk-adjusted
 RV_xSQ01ABC.m<-matrix(0,1,4) # Remaining Volatility
 PrBFDra_xSQ01ABC.m<-matrix(0,1,4) # Probability BFDra
 (AA_xSQ01ABC.m[1]<-c(42234.86)) #Y-end forecast & control after Q1
 (RE_xSQ01ABC.m[1]<- sum(E_xSQ01ABC.m[2:4]))
 (CF_xSQ01ABC.m[1]<-AA_xSQ01ABC.m[1]+RE_xSQ01ABC.m[1])
 (BFD_xSQ01ABC.m[1]<-CF_xSQ01ABC.m[1]-BudgetABC)
 (RV_xSQ01ABC.m[1]<- sqrt(sum(V_xSQ01ABC.m[2:4]^2)))
 (BFDra_xSQ01ABC.m[1]<-BFD_xSQ01ABC.m[1]/RV_xSQ01ABC.m[1])
 (PrBFDra_xSQ01ABC.m[1]<-pnorm(BFDra_xSQ01ABC.m[1]))
 (AA_xSQ01ABC.m[2]<-AA_xSQ01ABC.m[1]+c(33852.96))#Y-e.f.&ctr.after Q2
 (RE_xSQ01ABC.m[2]<- sum(E_xSQ01ABC.m[3:4]))
 (CF_xSQ01ABC.m[2]<-AA_xSQ01ABC.m[2]+RE_xSQ01ABC.m[2])
 (BFD_xSQ01ABC.m[2]<-CF_xSQ01ABC.m[2]-BudgetABC)
 (RV_xSQ01ABC.m[2]<- sqrt(sum(V_xSQ01ABC.m[3:4]^2)))
 (BFDra_xSQ01ABC.m[2]<-BFD_xSQ01ABC.m[2]/RV_xSQ01ABC.m[2])
 (PrBFDra_xSQ01ABC.m[2]<-pnorm(BFDra_xSQ01ABC.m[2]))


```
 






































