---
title: "IT-Based Management Summary"
author: "Group 06"
date: "11 12 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Forecasting and Probalistic Budgeting: Sales Volume Context (Learning with Case Studies)
\section{Use Case}
It is about Candle Manufacturing Inc. company, which produce three different candles like molded candles, solid candles and pulled candles. The company needs to setup the annual sales budget for the next year. To accomplish this, the traditional \textit{time series-based forecasting} methods are applied and two new approaches has been introduced: \newline
\textit{multinominal reggression-based} \newline
\textit{stochastic process-based forecasting of time series}\newline
To answer question about sales volumes that can expected for next year, the R software package are used as we can 
\begin{itemize}
\item perform a traditional time series analysis and use the model for \textbf{time series-based forecasting} for the next year
\item use timely intervals and perform a \textbf{regression-based forecasting}
\item read monthly sales from transactional data
\item perform a \textbf{stochastic process-based forecasting}
\item derive year-end forecast in fixed-event form
\item budget-forecast deviation with p-value to perform adjustments
\end{itemize}

\section {Problem Statement}
As there is uncertainity in business environment, the future predictation of sales volumes is also uncertain and time series-based approch forecast data with the help of historical data. It is not clear which time-based approch should be used in R to produce unbiased data. The two new approaches that are mentioned above allow additional forecast updating which are not possible in time series-based approches. Updating feature is very important in the fixed-event forecasting\footnote{ In the management control the fixed-event forecasts are the year-end forecasts} context as fixed time period is considered over time leading to a successively reducing of the lead time. 
\section {Contribution}
Traditional time series analysis covers the range between decomposition approaches, where non-stationary trends and seasonalities are included, and stationary ARIMA approaches. By introducing new modeling techniques in form of the multinomial regression-based and the stochastic processbased forecasting methods the time series modeling repertoire can be extended in
an effective and easy to grasp way.\newpage
\textbf{Result} 
\newline Multinomial regression-based and stochastic processbased forecasting are mathematically defined and statistically calibrated.
\section{Research Methodology}
The new artifacts are mathematically modeled and their applications are demonstrated in numerical examples.
\section{Research literature}
Hyndman Rob/Athanasopoulos George: Forecasting Principles and
Practice
Lawrence Michael/O???Connor Marcus: Sales forecasting updates:
how good are they in practice?
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
